\documentclass{report}

\usepackage{../../../../../LaTeX/marzstyle}

\newcommand{\exercisenr}{11}

\runningheads{Network Security}{Exercise \exercisenr}

\setcounter{chapter}{\exercisenr}
\setcounter{section}{0}


\begin{document}
	\section{Question 1}
	\startsection
		\renewcommand{\thesubsection}{\thesection.\Alph{subsection}}
		\subsection{RFC 5598 defines five components of the Internet Mail Architecture. In which order does a message pass through them on it's way from the sender to the receiver?}
		\begin{enumerate}
			\item Message User Agent
			\item Mail Submission Agent
			\item Message Transfer Agent
			\item Mail Delivery Agent
			\item Message Store
			\item[-] In the end the MUA is used to retrieve the messages from a remote server
		\end{enumerate}
		\subsection{Which of these components form the Message Handling System?}
		\startsubsection
			The Mail Submission Agent, the Message Transfer Agent, and the Mail Delivery Agent form the Message Handling System.
		\closesection
		\subsection{Which email protocols are used in the Internet Mail Architecture? Between which components are they used?}
		\startsubsection
			There are three common protocols used to deliver email over the internet:
			\begin{enumerate}
				\item Simple Mail Transfer Protocol (SMTP) \\
				Was designed as a host-to-host protocol in order to send messages directly to the destination
				\item Post Office Protocol (POP) \\
				Allows client to download email from a server.
				\item Internet Message Access Protocol (IMAP) \\
				Allows client to access email on an email server.
				\item[-] All of these protocols use TCP connections.
			\end{enumerate}
		\closesection
	\closesection
\end{document}